Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-05-17 Manuscript/01-Intro.Rmd
Edit Introduction

* Our method
* The implication of our method
* Structure of the rest of the paper

Nonlinear effect modeling has long history. Early work of GAMs can date back to 1979 when @Cleveland1979 proposed local smoothing for bivariate analysis. Many mathematical and statistical models has been proposed since, see xxx[^ TODO: insert an review citation].

Many machine learning algorithms can also model nonlinear effect. However, a wide range of machine learning models are confined by the "black box" nature, rendering little help on understanding the etiology of diseases. Semi-parametric and non-parametric regression models, are more popular thanks to its interpretability and flexibility. Among those, generalized additive model (GAM) proposed in the seminal work of @Hastie1987 gains the most popularity thanks to its flexibility and easiness to incorporate many different smoothing functions.  The backfitting algorithm estimates each smooth function of an additive model iteratively using partial residuals. The backfitting algorithm is compatible with almost any smoothing or modeling technique to be used as the nonparametric components. However, it is unclear how to estimate the degree of smoothness when necessary, for example for smoothing splines. The computation cost for cross-validating the smooth parameters can be expensive. @Wood2017[PP.318-320] provides more discussion on the problem.

Among all the choices of smoothing function, one particular family stood out, splines. Splines are piece-wise polynomial functions to interpolate nonlinear signals. Most commonly used spline is cubic spline, thanks to its smoothness property. [@Wood2017, PP.197] Early spline research focused on regression splines, where number and location of knots are pre-determined and ordinary least squares is used to estimate the smooth function. However, the specification of knots is not a trivial task, as the the positioning of knots are influential on the performance of the model. As an improvement, researchers proposed smoothing splines where as many knots are used and later shrunk using penalized algorithms. The smoothing spline concept was first introduced [@OSullivan1986; @OSullivan1988], and later generalized and made famous by @Eilers1996, called P-spline. Independently, @Ruppert1999 proposed similar idea. Later, Bayesian GAMs were introduced as an alternative to address measurement error in covariates [@Berry2002] or local adaptive smoothing [@Lang2004].

Generalized additive model (GAM) was first proposed by the seminal work: a response variable, $Y$, given a $p$-dimensional vector of covariates $\bm x$ can be expressed as the summation of smooth functions of $\bm x$, written as 
$$
E(Y|\bm x) = g^{-1}(a + \sum\limits^p_{j=1}f_j(x_j)),\qquad E[f_j(x_j)] = 0.
$$
where $g^{-1}$ is the inverse function of a smooth monotonic link function. Hence, GAM solve the model fitting problem for many distributional outcomes, such as Poisson, binomial, gamma and normal models. Since the appearance of GAMs, it has been applied in many area of research, such as xxx, xxx .

In many area of research, high dimensional analysis becomes predominant, for example sequencing data analysis, electric health record data analysis. Previous analysis heavily relies on linear models. Recently, there are more focus putting on modeling the non-linear relationships in high dimensional data analysis. Hence, developing more technically matured models is imminent. Nevertheless expanding the GAM framework for high-dimensional applications is not a trivial task. The difficulties mainly come in two-fold: grouping nature of the basis functions, and the balance between spline smoothness and variable sparsity. For GAM models, a smoothing function is consists of multiple basis functions. The basis functions of a variable is inherently grouped. The grouping structure should be properly taken care of for accurate estimation. Moreover, shrinkage is previously used solely for sparsity of the model in high dimensional data analysis, or smoothness in GAM models. How to organically combine the two together remains as a troubling question.

@@

The most distinct feature of the SS priors family is that it is conditioned on a latent binary variable $\gamma_i$ that indicates whether the covariate $x_i$ is included in the model. There are various spike-and-slab priors depending on the choice for the spike density $f_{spike}(\cdot)$ and the slab density $f_{slab}(\cdot)$, for example @George1993; @George1997; @Chipman1996 for grouped variables; @Brown1998 for multivariate outcomes; @Ishwaran2005; @Clyde2004 and reference therein. Here we introduce the most popular spike-and-slab prior introduced in @George1993, as  stochastic search variable selection (SSVS). Given a regression problem
$$
Y = \bm X\beta+\epsilon, 
$$
we can assume the prior distribution of the regression parameters $\beta$ depends on a vector of binary variables $\gamma=(\gamma_1, \dots \gamma_p)^\prime$ as follows: given $\gamma_i$, $\beta_i$ are independent distributed as a mixture priors
$$
\beta_i | \gamma_i \sim (1-\gamma_i)N(0, \sigma^2 v_0) + \gamma_iN(0,\sigma^2 v_1).
$$
The prior of $\gamma$ is traditionally assumed to be identically independent Bernoulli distribution. Even the conjugate normal prior of $\bm \beta$ provides analytic simplicity, there is no closed form solution for the posterior density of $\bm \gamma$. @George1993 described a Gibbs sampling algorithm to approximate the posterior distribution of $\bm \gamma$ for variable selection. The same authors later compared SSVS with other Bayesian variable selection approaches, providing some empirical suggestions on the advantages and disadvantages of various formulations and estimation algorithms. [@George1997] Among the various problem SSVS addresses, high-dimensionality is not one of them, due to the intensive computation needs of MCMC algorithms. @George1997 suggested MCMC algorithms works well for medium size of predictors (p=25), which is not feasible for high-dimensional data, where the number of predictors easily exceeds 100.

To alleviate the computation burden, many methodology development studies focus on the maximum a posteriori (MAP) estimate [@Tipping2004]. EM-based algorithms are prevalent used to speed the computation. @Rockova2014a proposed an EM-based algorithm for a spike-and-slab Gaussian mixture prior, EMVS. The coefficient $\beta_j$ independently follows a mixture normal distribution $N(0, \sigma^2((1-\gamma_i)v_0 + \gamma_i v_1)$ for $0 \leq v_0 < v_1$. The parameter $\sigma^2$ follows a inverse gamma prior, $IG(v/2, v\lambda /2)$. Like in the spike-and slab family, the latent binary variables $\bm \gamma$ follows a Bernoulli prior with a hyper prior $\theta$ follows a beta distribution, or simpler the uniform (0,1). In the E step, the latent variable are treated as the missing data, and calculate the posterior mean of $\gamma$; in the M step, a ridge estimator was used to update the coefficients, and $\sigma^2, \theta$ are updated accordingly. As the ridge regression creates small but nonzero coefficients, a further step is needed to select the variable: EMVS further suggests to threshold the inclusion probability for variable selection or generate regularization plot with different values of the spike scale parameter. EMVS is also compatible with structured prior when dealing with grouped variables. The group structure can be imposed on the prior of the latent binary variable $\gamma$ via either logistic regression or markov random field.

>>>>

* Our method
* The implication of our method
* Fast
* Structure of the rest of the paper

Nonlinear effect modeling has long history. Early work of GAMs can date back to 1979 when @Cleveland1979 proposed local smoothing for bivariate analysis. Since then, many mathematical and statistical models has been proposed, see xxx^[TODO: insert an review citation]. With recent advancement of computing technology, many machine learning algorithms that is computationally intensive start to gainmuch popularity in outcome prediction when non-linear effects assumed. Such models generally have improved prediction accuracy over classic statistical models, but have a fatal flaw, lack of transparency and interpretability. The primary objective of biomedical studies is to understand the etiology of diseases, which requires not only the knowledge if a biomarker is predictive of the disease, but also how the biomarker cause the disease. "Black box" models could less likely to be helpful.

As a balance between interpretability and model flexibility, semi-parametric and non-parametric regression models are studied. Among those, generalized additive model (GAM) proposed in the seminal work of @Hastie1987 gains the most popularity thanks to its flexibility and easiness to incorporate many different smoothing functions. A response variable, $Y$, that is assumed to follow some exponential family distribution $EF(\mu. \phi)$, can be expressed as the summation of smooth functions of a given $p$-dimensional vector of covariates $\bs x$, written as 
$$
E(Y|\bs x) = g^{-1}(a + \sum\limits^p_{j=1}f_j(x_j)),\qquad E[f_j(x_j)] = 0.
$$
where $g^{-1}$ is the inverse function of a smooth monotonic link function. GAM solves the model fitting problem for many distributional outcomes, such as Poisson, binomial, gamma and normal models. In the same article, @@Hastie1987 proposed the backfitting algorithm that estimates each smooth function of an additive model iteratively using partial residuals. The backfitting algorithm is compatible with almost any smoothing or modeling technique to be used as the nonparametric components. However, it is unclear how to estimate the degree of smoothness when necessary, for example for smoothing splines. The computation cost for cross-validating the smooth parameters can be expensive. @Wood2017[PP.318-320] provides more discussion on the problem.

In many area of modern biomedical research, dealing with high-dimensional data, also known as $p >> n$ problem, is common,  for example sequencing data analysis, electric health record data analysis. Many statistical models have been proposed for such problem, for example, penalized models and Bayesian hierarchical models. However, up to this point, most efforts of methodology development focus on modeling linear effect in high dimensional setting. It is still not clear what is the best practice on how to model non-linear effects in high-dimensional setting. Similar to expanding classic models to high-dimensional models, expanding the GAM framework for high-dimensional applications is not a trivial task. The difficulties mainly come in two-fold: grouping nature of the basis functions, and the balance between spline smoothness and variable sparsity. For GAM models, a smoothing function is consists of multiple basis functions. The basis functions of a variable is inherently related. The grouping structure should be properly taken care of for accurate estimation. Moreover, shrinkage is previously used solely for sparsity of the model in high dimensional regression models, or smoothness in GAMs. How to organically combine the two together remains as a troubling question.

<!-- Among all the choices of smoothing function, one particular family stood out, splines. Splines are piece-wise polynomial functions to interpolate nonlinear signals. Most commonly used spline is cubic spline, thanks to its smoothness property. [@Wood2017, PP.197] Early spline research focused on regression splines, where number and location of knots are pre-determined and ordinary least squares is used to estimate the smooth function. However, the specification of knots is not a trivial task, as the the positioning of knots are influential on the performance of the model. As an improvement, researchers proposed smoothing splines where as many knots are used and later shrunk using penalized algorithms. The smoothing spline concept was first introduced [@OSullivan1986; @OSullivan1988], and later generalized and made famous by @Eilers1996, called P-spline. Independently, @Ruppert1999 proposed similar idea. Later, Bayesian GAMs were introduced as an alternative to address measurement error in covariates [@Berry2002] or local adaptive smoothing [@Lang2004]. -->

@@

The most distinct feature of the SS priors family is that it is conditioned on a latent binary variable $\gamma_i$ that indicates whether the covariate $x_i$ is included in the model. There are various spike-and-slab priors depending on the choice for the spike density $f_{spike}(\cdot)$ and the slab density $f_{slab}(\cdot)$, for example @George1993; @George1997; @Chipman1996 for grouped variables; @Brown1998 for multivariate outcomes; @Ishwaran2005; @Clyde2004 and reference therein. Here we introduce the most popular spike-and-slab prior introduced in @George1993, as  stochastic search variable selection (SSVS). Given a regression problem
$$
Y = \bs X\beta+\epsilon, 
$$
we can assume the prior distribution of the regression parameters $\beta$ depends on a vector of binary variables $\gamma=(\gamma_1, \dots \gamma_p)^\prime$ as follows: given $\gamma_i$, $\beta_i$ are independent distributed as a mixture priors
$$
\beta_i | \gamma_i \sim (1-\gamma_i)N(0, \sigma^2 v_0) + \gamma_iN(0,\sigma^2 v_1).
$$
The prior of $\gamma$ is traditionally assumed to be identically independent Bernoulli distribution. Even the conjugate normal prior of $\bs \beta$ provides analytic simplicity, there is no closed form solution for the posterior density of $\bs \gamma$. @George1993 described a Gibbs sampling algorithm to approximate the posterior distribution of $\bs \gamma$ for variable selection. The same authors later compared SSVS with other Bayesian variable selection approaches, providing some empirical suggestions on the advantages and disadvantages of various formulations and estimation algorithms. [@George1997] Among the various problem SSVS addresses, high-dimensionality is not one of them, due to the intensive computation needs of MCMC algorithms. @George1997 suggested MCMC algorithms works well for medium size of predictors (p=25), which is not feasible for high-dimensional data, where the number of predictors easily exceeds 100.

To alleviate the computation burden, many methodology development studies focus on the maximum a posteriori (MAP) estimate [@Tipping2004]. EM-based algorithms are prevalent used to speed the computation. @Rockova2014a proposed an EM-based algorithm for a spike-and-slab Gaussian mixture prior, EMVS. The coefficient $\beta_j$ independently follows a mixture normal distribution $N(0, \sigma^2((1-\gamma_i)v_0 + \gamma_i v_1)$ for $0 \leq v_0 < v_1$. The parameter $\sigma^2$ follows a inverse gamma prior, $IG(v/2, v\lambda /2)$. Like in the spike-and slab family, the latent binary variables $\bs \gamma$ follows a Bernoulli prior with a hyper prior $\theta$ follows a beta distribution, or simpler the uniform (0,1). In the E step, the latent variable are treated as the missing data, and calculate the posterior mean of $\gamma$; in the M step, a ridge estimator was used to update the coefficients, and $\sigma^2, \theta$ are updated accordingly. As the ridge regression creates small but nonzero coefficients, a further step is needed to select the variable: EMVS further suggests to threshold the inclusion probability for variable selection or generate regularization plot with different values of the spike scale parameter. EMVS is also compatible with structured prior when dealing with grouped variables. The group structure can be imposed on the prior of the latent binary variable $\gamma$ via either logistic regression or markov random field.

### 2021-05-17 Manuscript/02-Method.Rmd
Edit Introduction

$$
\begin{aligned}
p(\bs \beta | \bs\gamma) &\propto \prod\limits_{j=1}^{p}\left[{S^0_j}^{-1/2}\exp(-1/2({\beta^0_{j}}^2/S^0_{j}))\prod\limits_{k=1}^{K_j}S_{j}^{-1/2}\exp(-1/2(\beta_{jk}^2/S_{j}))\right],%\\
% p(\bs\gamma | \bs \theta) & = \prod\limits_{j=1}^{p}\prod\limits_{k=1}^{K_j} \theta_j^{\gamma_{jk}} (1-\theta_j)^{1-\gamma_{jk}}.
\end{aligned}
$$
and 
$$
\begin{aligned}
E(Q_1) &= \log p(\textbf{y}|\bs \beta, \phi) + \log p(\phi) + \sum\limits_{j=1}^p\left[E({S^0_j}^{-1}){\beta^0_j}^2+\sum\limits_{k=1}^{K_j}E(S^{-1}_{j})\beta_{jk}^2\right]%\\
%E(Q_2) &= \sum\limits_{j=1}^{p}\sum\limits_{k=1}^{K_j} \left[ E(\gamma_{jk})\log \theta_j + (1-E(\gamma_{jk})) \log (1-\theta_j)\right] +  \sum\limits_{j=1}^{p}\log p(\theta_j)
\end{aligned}
$$
where $S_{j}^0 = (1-\gamma^{0}_{j}) s_0 + \gamma^{0}_{j} s_1$ and $S_{j} = (1-\gamma^{pen}_{j}) s_0 + \gamma^{pen}_{j} s_1$. To calculate two unknown quantities $E({S_j^0}^{-1})$ and $E(S^{-1}_j)$, the posterior probability $p^0_{j} \equiv p(\gamma^{0}_{j}=1|\Theta^{t-1})$ and $p_{j} \equiv p(\gamma^{pen}_{j}=1|\Theta^{t-1})$ are necessary, which can be derived via Bayes' theorem. The calculation for $p_j$ is slightly different from that of $p^0_j$, as $p_j$ depends on the value of $\beta_{jk}$ for $k=1, \dots, K_j$ and $p^0_j$ only depends on $\beta_j^0$. The calculation follows the equations below.

@@

With $E({S^0}^{-1}_{j})$ and $E(S^{-1}_{j})$ known, $E(Q_1)$ can be also viewed as a $l_2$ penalized likelihood function: $E({S^0}^{-1}_{j})$ controls the shrinkage of the linear effect, informing if the predictor should be included in the model; $E(S^{-1}_{j})$ controls the smoothness of the spline function. $l_2$ penalized likelihood function can be maximize using the IWLS algorithm.  The likelihood function can be approximate by a weighted normal likelihood:
$$
  p(\textbf{y}|\bs \beta, \phi) \approx Normal(\textbf{z}|X\beta, \phi\Sigma)
$$
    where the ‘normal response’ $z_i$ and ‘weight’ $w_i$ are called the pseudo-response and pseudo-weight, respectively.The pseudo data and the pseudo-weight are calculated by
    $$
    \begin{aligned}
    z_i &= \hat\eta_i - \frac{L^{'}((y_i|\hat\eta_i))}{L^{''}((y_i|\hat\eta_i))}& w_i &= - L^{''}((y_i|\hat\eta_i)),
    \end{aligned}
    $$
    where $\eta_i = \sum\limits_{j=1}^p \hat f_j^{(t)}(x_{ij})$ is the estimated linear predictor using current estimated value of $\bs \beta$, $L^{'}$ and $L^{''}$ are the first derivative and second derivative of the log-likelihood function. The $l_2$ penalty, $ \sum\limits_{j=1}^p\left[E({S^0_j}^{-1}){\beta^0_j}^2+\sum\limits_{k=1}^{K_j}E(S^{-1}_{j})\beta_{jk}^2\right]$ can be seems as a multivariate normal distribution of mean $\textbf{0}$ and variance-covariance matrix $\Sigma(E({S^0}_1^{-1}), E(S_1^{-1}), \dots, E({S_p^0}^{-1}), E(S_p^{-1})$, conditioning on the value of $E({S^0_1}^{-1}), \dots E({S^0_p}^{-1})$. An augmentation step combines the normal approximation and multivariate normal for $\bs \beta$, similarly to Ridge regression model fitting. The estimates of $\bs \beta$ and $\phi$ can be quickly updated in the IRLS algorithm.

>>>>

$$
\begin{aligned}
p(\bs \beta | \bs\gamma) &\propto \prod\limits_{j=1}^{p}\left[{S^0_j}^{-1/2}\exp(-1/2({\beta^0_{j}}^2/S^0_{j}))\prod\limits_{k=1}^{K_j}S_{j}^{-1/2}\exp(-1/2(\beta_{jk}^2/S_{j}))\right],%\\
% p(\bs\gamma | \bs \theta) & = \prod\limits_{j=1}^{p}\prod\limits_{k=1}^{K_j} \theta_j^{\gamma_{jk}} (1-\theta_j)^{1-\gamma_{jk}}.
\end{aligned}
$$
and 
\begin{align*}
E(Q_1) &= \log p(\textbf{y}|\bs \beta, \phi) + \log p(\phi) + \sum\limits_{j=1}^{p} \left[E({S^0_j}^{-1}){\beta^0_j}^2+\sum\limits_{k=1}^{K_j}E(S^{-1}_{j})\beta_{jk}^2\right]\\
E(Q_2) &= \sum\limits_{j=1}^{p}\sum\limits_{k=1}^{K_j} \left[ E(\gamma_{jk})\log \theta_j + (1-E(\gamma_{jk})) \log (1-\theta_j)\right] +  \sum\limits_{j=1}^{p}\log p(\theta_j)
\end{align*}
where $S_{j}^0 = (1-\gamma^{0}_{j}) s_0 + \gamma^{0}_{j} s_1$ and $S_{j} = (1-\gamma^{pen}_{j}) s_0 + \gamma^{pen}_{j} s_1$. To calculate two unknown quantities $E({S_j^0}^{-1})$ and $E(S^{-1}_j)$, the posterior probability $p^0_{j} \equiv p(\gamma^{0}_{j}=1|\Theta^{t-1})$ and $p_{j} \equiv p(\gamma^{pen}_{j}=1|\Theta^{t-1})$ are necessary, which can be derived via Bayes' theorem. The calculation for $p_j$ is slightly different from that of $p^0_j$, as $p_j$ depends on the value of $\beta_{jk}$ for $k=1, \dots, K_j$ and $p^0_j$ only depends on $\beta_j^0$. The calculation follows the equations below.

@@

With $E({S^0}^{-1}_{j})$ and $E(S^{-1}_{j})$ known, $E(Q_1)$ can be also viewed as a $l_2$ penalized likelihood function: $E({S^0}^{-1}_{j})$ controls the shrinkage of the linear effect, informing if the predictor should be included in the model; $E(S^{-1}_{j})$ controls the smoothness of the spline function. $l_2$ penalized likelihood function can be maximize using the IWLS algorithm.  The likelihood function can be approximate by a weighted normal likelihood:
$$
  p(\textbf{y}|\bs \beta, \phi) \approx Normal(\textbf{z}|X\beta, \phi\Sigma)
$$
    where the ‘normal response’ $z_i$ and ‘weight’ $w_i$ are called the pseudo-response and pseudo-weight, respectively.The pseudo data and the pseudo-weight are calculated by
    $$
    \begin{aligned}
    z_i &= \hat\eta_i - \frac{L^{'}((y_i|\hat\eta_i))}{L^{''}((y_i|\hat\eta_i))}& w_i &= - L^{''}((y_i|\hat\eta_i)),
    \end{aligned}
    $$
    where $\eta_i = \sum\limits_{j=1}^p \hat f_j^{(t)}(x_{ij})$ is the estimated linear predictor using current estimated value of $\bs \beta$, $L^{'}$ and $L^{''}$ are the first derivative and second derivative of the log-likelihood function. The $l_2$ penalty, $\sum\limits_{j=1}^{p}\left[E({S^0_j}^{-1}){\beta^0_j}^2+\sum\limits_{k=1}^{K_j}E(S^{-1}_{j})\beta_{jk}^2\right]$ can be seems as a multivariate normal distribution of mean $\textbf{0}$ and variance-covariance matrix $\Sigma(E({S^0}_1^{-1}), E(S_1^{-1}), \dots, E({S_p^0}^{-1}), E(S_p^{-1})$, conditioning on the value of $E({S^0_1}^{-1}), \dots E({S^0_p}^{-1})$. An augmentation step combines the normal approximation and multivariate normal for $\bs \beta$, similarly to Ridge regression model fitting. The estimates of $\bs \beta$ and $\phi$ can be quickly updated in the IRLS algorithm.

### 2021-05-17 Manuscript/main.Rmd
Edit Introduction

---
title: A demonstration of the \LaTeX class file for Statistics in Medicine with Rmarkdown
author:
- name: Boyi Guo*
  num: a
- name: Nengjun Yi
  num: a
address:
- num: a
  org: Department of Biostatistics, University of Alabama at Birmingham, Birmingham, USA
# - num: b
  # org: Department of Applied Things, University B, City B, Country B
corres: "*Corresponding author name, This is sample corresponding address. \\email{xxx@uab}"
presentaddress: This is sample for present address text this is sample for present address text
authormark: Guo and Yi
articletype: Research article
received: 2017-01-01
revised: 2017-02-01
accepted: 2017-03-01
abstract: "TODO: Change this accordingly; Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean ut elit odio. Donec fermentum tellus neque, vitae fringilla orci pretium vitae. Fusce maximus finibus facilisis. Donec ut ullamcorper turpis. Donec ut porta ipsum. Nullam cursus mauris a sapien ornare pulvinar. Aenean malesuada molestie erat quis mattis. Praesent scelerisque posuere faucibus. Praesent nunc nulla, ullamcorper ut ullamcorper sed, molestie ut est. Donec consequat libero nisi, non semper velit vulputate et. Quisque eleifend tincidunt ligula, bibendum finibus massa cursus eget. Curabitur aliquet vehicula quam non pulvinar. Aliquam facilisis tortor nec purus finibus, sit amet elementum eros sodales. Ut porta porttitor vestibulum. Integer molestie, leo ut maximus aliquam, velit dui iaculis nibh, eget hendrerit purus risus sit amet dolor. Sed sed tincidunt ex. Curabitur imperdiet egestas tellus in iaculis. Maecenas ante neque, pretium vel nisl at, lobortis lacinia neque. In gravida elit vel volutpat imperdiet. Sed ut nulla arcu. Proin blandit interdum ex sit amet laoreet. Phasellus efficitur, sem hendrerit mattis dapibus, nunc tellus ornare nisi, nec eleifend enim nibh ac ipsum. Aenean tincidunt nisl sit amet facilisis faucibus. Donec odio erat, bibendum eu imperdiet sed, gravida luctus turpis."
keywords: Class file; \LaTeX; Statist. Med.; Rmarkdown;
bibliography: bibfile.bib
output: 
  rticles::sim_article:
    keep_tex: TRUE
---

@@

# References
<div id="refs"></div>

>>>>

---
title: Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data
author:
- name: Boyi Guo*
  num: a
- name: Nengjun Yi
  num: a
address:
- num: a
  org: Department of Biostatistics, University of Alabama at Birmingham, Birmingham, USA
# - num: b
  # org: Department of Applied Things, University B, City B, Country B
corres: "*Corresponding author name, This is sample corresponding address. \\email{xxx@uab}"
presentaddress: This is sample for present address text this is sample for present address text
authormark: Guo and Yi
articletype: Research article
received: 2021-01-01
revised: 2021-02-01
accepted: 2021-03-01
abstract: "Spike-and-slab priors have been extensively studied for variable selection, and recently been extended to function selection in generalized additive models (GAMs). Most of the previous works on fitting spike-and-slab GAM relies on Markov chain Monte Carlo (MCMC) algorithms to identify the promising subsets of functions. The computational burden of MCMC makes these models less feasible, especially in high-dimensional setting. Besides, most of the current spike-and-slab GAM consider an “all-in-all-out” approach for function selection, rendering less flexibility to answer if non-linear effects are necessary in the model. We propose Bayesian hierarchical generalized additive models for function selection and prediction. The proposed models employ spike-and-slab priors, mixture normal and mixture double exponential, for smooth and sparse solution. Two EM based algorithms, EM-IWLS and EM-Coordinate Descent, are developed for accelerated computation. Simulation studies and real data analysis demonstrated improved performance against the state-of-art models, mgcv and COSSO. The software implementation of the proposed methods is freely available via the R package BHAM."
keywords: Spike-and-Slab Priors; High-Dimensional Data; Generalized Additive Models; EM-IWLS; EM-Coordinate Decent
bibliography: bibfile.bib
output: 
  rticles::sim_article:
    keep_tex: TRUE
---

@@

# References
